INSERT

### 2022-12-12 paper.Rmd
Updated Introduction

@@

One of North America's most noticeable symptoms of climate change has been a dramatic increase in the volume and intensity of wildfires, particularly in its western regions. August and September were previously defined by clear skies and fair weather, but fire and smoke have become a recurrent factor in this area. According to the National Interagency Fire Center (NIFC), more acreage burned nationally in each of the last seven years than any single year but one in the first ten years this data was collected (1983-1993, ex. 1988).^[See https://www.nifc.gov/fire-information/statistics/wildfires.] We sought to analyze if and how public sentiment has shifted over time with respect to these cataclysmic events, with the hopes of gaining some insight into public perceptions of climate change.

@@

@@

@@

@@

@@

>>>>

## Abstract

@@

One of North America's most noticeable symptoms of climate change has been a dramatic increase in the volume and intensity of wildfires, particularly in its western regions. August and September were previously defined by clear skies and fair weather, but fire and smoke have become a recurrent factor in this area. According to the National Interagency Fire Center (NIFC), more acreage burned nationally in each of the last seven years than any single year but one in the first ten years this data was collected (1983-1993, ex. 1988).^[See https://www.nifc.gov/fire-information/statistics/wildfires.] With more and more people affected by the increase in wildfire activity, it's reasonable to infer an increasing outcry of negativity towards this devastating symptom of climate change. However, it is hypothesized that the negative outcry may only come from people directly affected by the fire. An, "out of sight, out of mind", mentality may be prevalent in the United States, particularly around the affects of wildfires. We explored four recent US wildfires, that took place sequentially with the past 5 years, to analyze if and how public sentiment has shifted over time with respect to these cataclysmic events. Specifically, we sought to answer the following two questions.

* How has public sentiment towards wildfires changed in the past 5 years?

* Is this change regionalized? Is public sentiment only shifted by those directly affected by these devastating events?

We compared two different sentiment analysis algorithms in hopes of gaining some insight into public perceptions of climate change.

@@

# Sentiment Analysis

@@

# Change through time

@@

# Effect of location

@@

# Effect of Location

# Comparison of Sentiment Analysis Algorithm

@@

[Add subheaders for each section]
